Knowledge Representation for Service Robots: Supply and Demand

### 2014-04-16 krs-survey.tex
Table of systems fit on a double column

\begin{landscape}
\begin{table}\scriptsize
\begin{center}

\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}lp{2.4cm}p{3.4cm}p{1.5cm}}
\toprule
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Project homepage} & {\bf Programming language} & {\bf Knowledge model/Logical Formalism} & Main reference \\
\midrule
ARMAR/Tapas & Formal & Holzapfel, Waibel \par (Karlsruhe TH) & & & TFS (Typed Feature Structures) & \cite{Holzapfel2008}\\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ., DFKI Saarbrücken) & & & Amodal proxies & \cite{Jacobsson2008} \\
GSM & Structural & Mavridis, Roy \par (MIT MediaLab) & & & & \cite{Mavridis2006} \\
Ke Jia Project & Formal & Chen et al. \par (Univ. of Science and Technology of China) & \url{www.wrighteagle.org/en} & ASP (Answer Set Programming) & ASP & \cite{Chen2010} \\
{\sc KnowRob} & Formal & Tenorth, Beetz \par (TU Munich) & \url{ias.in.tum.de/kb/wiki} & {\sc Prolog} & {\sc Prolog} + OWL-DL &  \cite{Tenorth2009a} \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & & NKRL & & \cite{Sabri2011} \\
%OBOC & KRS & Mendoza & & & & & \cite{Mendoza2005} \\
ORO & Formal & Lemaignan, Alami \par (LAAS-CNRS) & \url{oro.openrobots.org} & {\sc Java} & OWL-DL ({\sc Jena}) + {\sc Pellet} & \cite{Lemaignan2010} \\
OUR-K/OMRKF & Formal & Lim, Suh et al. \par (Hanyang Univ.) & \url{incorl.hanyang.ac.kr/xe} & ? & DL + Horn Clauses &  \cite{Lim2011, Suh2007} \\
PEIS KR\&R & Formal & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & \url{www.aass.oru.se/~peis} & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & \cite{Daoutis2009} \\
%Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
% & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\ % -> affordances, but no implementation on a robot
% & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\ % -> mostly planning under uncertainty
% & & Hertzberg (Osnabrück Univ.) \\ % -> affordances, semantic mapping
% (based on {\sc KnowRob} & & (JSK) \\

@@

\label{table|surveyed-systems}
\end{table}
\end{landscape}

>>>>

\begin{table*}\scriptsize
\begin{center}

\begin{tabular}{p{2.2cm}p{1.6cm}p{4cm}p{2.4cm}p{3.4cm}p{1.5cm}}
\toprule
{\bf Project} & {\bf Category} & {\bf Authors (Institution)} & {\bf Programming language} & {\bf Knowledge model/Logical Formalism} & Main reference \\
\midrule
ARMAR/Tapas & Formal & Holzapfel, Waibel \par (Karlsruhe TH) & & TFS (Typed Feature Structures) & \cite{Holzapfel2008}\\
CAST Proxies & Ubiquitous & Wyatt, Hawes, Jacobsson, Kruijff (Brimingham Univ.,
DFKI Saarbrücken) & & Amodal proxies & \cite{Jacobsson2008} \\
GSM & Structural & Mavridis, Roy \par (MIT MediaLab) & & & \cite{Mavridis2006} \\
Ke Jia Project & Formal & Chen et al. \par (Univ. of Science and Technology of China) & ASP (Answer Set Programming) & ASP & \cite{Chen2010} \\
{\sc KnowRob} & Formal & Tenorth, Beetz \par (TU Munich) & {\sc Prolog} & {\sc Prolog} + OWL-DL &  \cite{Tenorth2009a} \\
NKRL & Language & Zarri et al. \par (Paris Est Créteil Univ.) & NKRL & & \cite{Sabri2011} \\
%OBOC & KRS & Mendoza & & & & & \cite{Mendoza2005} \\
ORO & Formal & Lemaignan, Alami \par (LAAS-CNRS) & {\sc Java} & OWL-DL ({\sc Jena}) + {\sc Pellet} & \cite{Lemaignan2010} \\
OUR-K/OMRKF & Formal & Lim, Suh et al. \par (Hanyang Univ.) & ? & DL + Horn Clauses &  \cite{Lim2011, Suh2007} \\
PEIS KR\&R & Formal & Daoutis, Coradeshi, Loutfi, Saffiotti \par (Örebro Univ.) & {\sc C}, {\sc CycL} & CycL (1st and 2nd order logics, modal logics) & \cite{Daoutis2009} \\
%Golog & Language & Levesque (Toronto Univ.) & & {\sc Prolog} & & & \\
% & & Varadarajan, Vincze \par (TU Wien) & & & & & \cite{Varadarajan2011} \\ % -> affordances, but no implementation on a robot
% & & Kaelbling, Lozano-Pérez \par (MIT CSAIL) & & & & & \cite{Kaelbling2011} \\ % -> mostly planning under uncertainty
% & & Hertzberg (Osnabrück Univ.) \\ % -> affordances, semantic mapping
% (based on {\sc KnowRob} & & (JSK) \\

@@

\label{table|surveyed-systems}
\end{table*}
